\documentclass[12pt]{letter}

% Change bracketd option in brackets for alternate letterhead
\usepackage[cis]{bowersletterhead}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{etoolbox}
\usepackage{hyperref}
%\usepackage[cs]{bowersletterhead}
%\usepackage[cornell]{bowersletterhead}
%\usepackage[is]{bowersletterhead}
%\usepackage[sds]{bowersletterhead}

%% LOGIC FOR CUSTOMIZING THE STATEMENT FOR INDIVIDUAL SCHOOLS
% set up common defines (commands and boolean flags)
\input{../defines.tex}
% import the school-specific header to make the magic happen!
\input{schoolheader.tex}
%% END CUSTOMIZATION LOGIC

\myname{Jonathan P. Chang}
\mytitle{Ph.D. Candidate}
\myemail{jpc362@cornell.edu}
\mywebsite{\href{https://cs.cornell.edu/~jpchang}{cs.cornell.edu/\char`~jpchang}}
\myroomnumber{214 Gates Hall}
\myphonenumber{+1 (408) 717-1539}

\begin{document}

\signature{Jonathan P. Chang}
\begin{letter}{
\ifundef{\chairname}{Faculty Search Committee\\}{\chairname\\\chairtitle\\}
\department \\
\schoolnamelong \\
\schooladdress
}

\opening{
    Dear \ifundef{\chairlastname}{Members of the Search Committee}{\chairlastname and Members of the Search Committee},
}

I am writing to apply for the position of \position.
I am currently a Ph.D. candidate in Computer Science at Cornell University, with an expected graduation date of May 2024.
Advised by Prof. Cristian Danescu-Niculescu-Mizil, I work at the intersection of Natural Language Processing and Computational Social Science.
The Claremont Colleges play a special role in my academic journey, as an alumnus of Harvey Mudd College, and I feel uniquely positioned to contribute back to Claremont by bringing to Pomona my interdisciplinary research agenda and passion for teaching.

% teaching paragraph
For me to teach at Pomona would be to bring my journey as an educator full circle: my overall teaching philosophy is directly inspired by my Claremont education, which included a number of courses at Pomona.
It is therefore no surprise that the concrete teaching strategies I use (see Teaching Statement) directly mirror aspects of Pomona's CS curriculum.
For example, consider my use of narratives to ground abstract CS concepts in concrete examples that connect to real-world applications.
This strategy parallels the design of Pomona's intro CS courses (CSCI 051x), which similarly motivate core CS concepts via real-world applications, both through hands-on laboratory exercises and connections to topics in AI (051A).
As someone who is particularly excited about teaching intro-level CS, I would look forward to the opportunity to teach any of the CSCI 051x courses, alongside other intro-sequence courses like CSCI 062.
Of course, I would also be interested in teaching higher-level courses connected to my research agenda, such as \schooladvcourses.
Finally, I am prepared to develop a new course on Computational Social Science, a growing interdisciplinary field of research that fits well with the Liberal Arts mission of Pomona and Claremont.

% research paragraph
My research also embodies the interdisciplinary spirit of the Claremont Colleges and Liberal Arts more broadly: I study online community governance and content moderation from a combined technical and social perspective.
On the technical side, I develop novel computational models of online interaction that can help identify situations at risk of escalating into toxic or offensive behavior.
On the social side, I collaborate with real online communities to evaluate how this technology could help their users have healthier online interactions.
This focus on real-world applications opens up opportunities for undergraduate students to contribute in both software development and research design, as shown by the experiences of the six undergraduate and five masters students I have mentored---one of whom led a major user study and was first author on the resulting peer-reviewed academic conference paper.
This cutting-edge research agenda, which has led not only to various peer-reviewed publications in top-tier venues but also spawned a completely new NLP task (detailed in my Research Statement), is a strong fit for an institution like Pomona that prides itself on high-quality research.

Included in my application are the following materials: \materials
For references, you may contact Profs. Cristian Danescu-Niculescu-Mizil, Karen Levy, and Peter Enns from Cornell University.
Thank you for your consideration, and I look forward to hearing back from you.

\closing{Sincerely,}

\end{letter}
\end{document}
