\renewcommand{\schoolname}{Union\xspace}
\renewcommand{\schoolnamelong}{Union College\xspace}
\renewcommand{\schooladdress}{807 Union Street, Schenectady, NY 12308\xspace}
\renewcommand{\schoolintrocourses}{CSC 103-108, CSC 120, and CSC 151\xspace}
\renewcommand{\schooladvcourses}{CSC 320: Artificial Intelligence, CSC 321: Data Mining and Machine Learning, and CSC 329: Neural Networks\xspace}
\let\chairname\relax
\let\chairlastname\relax
\let\chairtitle\relax
\renewcommand{\position}{Assistant Professor of Computer Science (Job No. 493331)\xspace}
\longdeifalse
\appendixtrue
\liberalartstrue

\renewcommand{\materials}{my latest CV and statements on teaching and research.\xspace}

\renewcommand{\coverteachingpara}{%
I am drawn to Union because I see this core principle reflected in the design of its CS curriculum.
In particular, I am very interested in Union's themed approach to introductory CS (the CSC 103-108 series), which closely mirrors my own teaching philosophy of anchoring CS concepts in concrete examples and narratives from real-world applications (discussed further in my Teaching Statement).
I am passionate about teaching at the intro level, and within the Union intro sequence I am most qualified to teach CSC 103, CSC 106, and CSC 108.
I would also be excited to teach other foundational CS courses like CSC 120 and CSC 151, as well as more advanced courses connected to my research interests, such as \schooladvcourses.
Finally, I would love the chance to share my specific research interests, Natural Language Processing and Computational Social Science, with Union's students, either through developing new courses or as sections of the Selected Topics course CSC 483.
In teaching any of these courses, I would maintain my commitment to creating inclusive learning environments that are accessible and welcoming to students of all backgrounds, as I detail in my Teaching Statement.%
}

\renewcommand{\coverresearchpara}{%
I believe this research agenda fits well with Union's inderdisciplinary spirit, and in particular would offer excellent research opportunities for students pursuing an interdepartmental major.%
}